---
name: John Paul
surname: Broussard
position: "Finance Professor with Decades of Superior Administrative, Research, and Teaching Experiences"
address: "Oklahoma City, Oklahoma, USA"
profilepic: "./img/jaafGalaPic.jpg"
www: "tinyurl.com/c3wdneyp"
email: "john.broussard@rutgers.edu"
linkedin: "tinyurl.com/5bfex8hv"
orcid: 0000-0002-5090-9947
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 990000
aboutme: "I am a Finance Professor with over 25 years of extensive domestic and international experience in online and traditional academic program management. I create academic programs and courses that monetize academic effort and yield institutional revenue enhancement and stakeholder success. I maintain real-world relevance through being a Financial Professional Designation Exam Trainer, Financial Risk Management Specialist, Financial Market Consultant, Expert on Big Data, Implementer of Natural Language Processing, Artificial Intelligence and Machine Learning applications in Finance."
docname: jpbDataDrivenCV
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

require(xfun)

packages <- c('vitae'     # The CV's LaTeX Template
             ,'tibble'    # Data structure for tribbles
             ,'magrittr'  # The Pipe %>%
             ,'here'      # Relative File Paths
             ,'readr'     # Data Loading
             ,'glue'      # String Manipulation
            )

xfun::pkg_attach2(packages, message = FALSE)

if (file.exists(here("cv_data.rds"))) {
  cv_data <- readRDS(here("cv_data.rds"))
  for (nm in names(cv_data)) assign(nm, cv_data[[nm]])
  rm(cv_data)
} else {
  source(file = here("jpbsCVdata", "jpbsCVdata.r"))
}

```

# ADMINISTRATIVE EXPERIENCE

```{R ADMINISTRATIVE}

admin %>%
    detailed_entries(
        with = institution,
        what = title,
        why = detail
    )
```

# LONG-TERM ACADEMIC APPOINTMENTS

```{r LTEMPLOYMENT}

ltWork %>%
  detailed_entries(
    with = institution,
    #what = title,
    why = detail,
    when = glue::glue("{startMonth} {startYear} --> {endMonth} {endYear}",.na = ""),
    where = where
  )

```

# SHORT-TERM ACADEMIC APPOINTMENTS

```{r STEMPLOYMENT}

stWork %>%
  detailed_entries(
    with = institution,
    #what = title,
    why = detail,
    when = glue::glue("{startMonth} {startYear} --> {endMonth} {endYear}",.na = ""),
    where = where
  )

```

# EDUCATION

```{r EDUCATION}

edu %>%
  detailed_entries(
    with = inst,
    what = degree,
    why = detail,
    when = glue::glue("{startYear} --> {endYear}",.na = ""),
    where = where
  )

```

# PROFESSIONAL CERTIFICATIONS

```{r CERTIFICATIONS}

certifications %>%
  detailed_entries(
    with = certBody,
    what = accomplishment,
    why = detail,
    when = year,
    where = where
  )

```

# HONORS and GRANTS

```{r HONORS}

honorsGrants %>%
  detailed_entries(
    with = honorGrant,
    what = grantor,
    why = detail,
    when = year,
    where = where
  )

```

# PEER-REVIEWED PUBLICATIONS

```{r PUBLICATIONS}

publications %>%
  detailed_entries(
    with = articleTitle,
    what = authors,
    why = journal,
    when = year
  )
```

# Projects in Progress

```{r PIP}

pip %>%
  detailed_entries(
    with = articleTitle,
    what = authors,
    why = status
  )

```

# Other Publications and Monographs

```{r OPM}

otherPubsMonos %>%
  detailed_entries(
    with = title,
    what = authors,
    why = outlet,
    when = year
  )

```

# ACADEMIC CONFERENCE ACTIVITIES

## Presented Papers

```{r PRESENTATIONS}

academicPresents %>%
  detailed_entries(
    with = articleTitle,
    what = authors,
    why = detail
  )

```

------------------------------------------------------------------------

## Pedagogical Presentations

```{r PEDAGOGYPRSENTS}

pedagogyPresents %>%
  detailed_entries(
    with = title,
    where = detail
  )

```

------------------------------------------------------------------------

## Discussed Papers

```{r DISCUSSIONS}

academicDiscussions %>% 
  detailed_entries(
    with = articleTitle, 
    what = authors, 
    why = detail
  )

```

------------------------------------------------------------------------

## Conference Committees

```{r CONFCOMM}

confCommittees %>%
  detailed_entries(
    with = conference,
    what = role,
    where = details
  )
```

------------------------------------------------------------------------

## Conference Session Chair

```{r CONFCHAIR}

confChair %>%
  detailed_entries(
    with = conference,
    where = details
  )

```

# SERVICE ACTIVITIES

## Profession - Editorships

```{r EDITING}

editor %>%
  detailed_entries(
    with = role,
    what = journal,
    when = glue::glue("{begYear} --> {endYear}",.na = "")
  )

```

------------------------------------------------------------------------

## Profession - Ad Hoc Reviewer

```{r ADHOCREVIEW}

adHocReview %>% 
  detailed_entries(
    what = outletName,
    when = outletType
  )

```

------------------------------------------------------------------------

## Profession - Promotion/Appointment Review

```{r TANDP}

tAndP %>%
  detailed_entries(
    with = task,
    what = school,
    when = year,
    why = role
  )
```

------------------------------------------------------------------------

## Profession - Association Offices Held

```{r PROFOFFICES}
profesionalOFfices %>% 
  detailed_entries(
    with = title,
    what = group,
    when = glue::glue("{begYear} --> {endYear}",.na = "")
    
  )

```

------------------------------------------------------------------------

## Institutional Leadership Roles

```{r LEADER}

academicLeader %>%
  detailed_entries(
    with = title,
    what = school,
    when = glue::glue("{begYear} --> {endYear}",.na = "")
  )

```

------------------------------------------------------------------------

## Institutional Committee Participation

```{r COMMITTEES}

academicCommittees %>%
  detailed_entries(
    with = committeeName,
    what = institution,
    when = glue::glue("{begYear} --> {endYear}",.na = "")
    
  )


```

# STUDENT ACTIVITIES

## Dissertation Committees

```{r DISSERTATIONS}

dissertationCommittees %>% 
  detailed_entries(
    with = student,
    what = dissTitle,
    why = school,
    when = year,
    where = role
  )


```

------------------------------------------------------------------------

## Thesis/Non-PhD Research Supervision

```{r THESES}
thesesSupervision %>% 
  detailed_entries(
    with = student,
    what = thesisTitle,
    why = school,
    when = year,
    where = role
  )

```

------------------------------------------------------------------------

## Student Mentoring

```{r MENTORING}
studentMentoring %>% 
  detailed_entries(
    with = activity,
    what = school,
    when = glue::glue("{begYear} --> {endYear}",.na = ""),
    why = role
    
  )
```

# Professional Seminars and Training

```{r PROFTRAINING}
profTraining %>% 
  detailed_entries(
    with = activity,
    what = group,
    when = glue::glue("{begYear} --> {endYear}",.na = ""),
    why = role
  )

```

# Media Interviews

```{r MEDIAINTS}
mediaInterviews %>% 
  detailed_entries(
    with = topic,
    what = modality,
    why = outlet,
    when = glue::glue("{year}",.na="")
  )


```

# Business Experiences

```{r BIZ}
bizExperiences %>%  
  detailed_entries(
    with = title,
    what = company,
    when = glue::glue("{begYear} --> {endYear}",.na = "")
  )

```

\pagebreak

# REFERENCES

```{r REFERENCES}
references %>% 
  detailed_entries(
    with = name,
    what = title,
    why = details
  )

```
