---
title: "John Paul Broussard"
subtitle: |
  Finance Professor | Academic Administrator | Research Leader  
  Willis, Texas, USA
format:
  pdf:
    documentclass: article
    geometry:
      - top=0.75in
      - bottom=0.75in
      - left=0.75in
      - right=0.75in
    fontsize: 10pt
    linestretch: 1.1
    include-in-header:
      text: |
        \usepackage{titlesec}
        \usepackage{enumitem}
        \usepackage{fancyhdr}
        \usepackage{hyperref}
        \usepackage{xcolor}
        \definecolor{darkblue}{RGB}{44,95,124}
        \hypersetup{colorlinks=true, linkcolor=darkblue, urlcolor=darkblue}
        \pagestyle{fancy}
        \fancyhf{}
        \renewcommand{\headrulewidth}{0pt}
        \cfoot{\thepage}
        \titleformat{\section}{\large\bfseries\color{darkblue}}{\thesection}{1em}{}[\titlerule]
        \titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}
        \titlespacing{\section}{0pt}{*2}{*1.5}
        \titlespacing{\subsection}{0pt}{*1.5}{*1}
        \setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=1pt}
execute:
  echo: false
  warning: false
  message: false
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(here)
library(glue)

# Load CV data with correct path
if (file.exists("jpbsCVdata/load_cv_data.r")) {
  source("jpbsCVdata/load_cv_data.r")
  cv_data <- load_cv_data()
  list2env(cv_data, envir = .GlobalEnv)
}

# Set options
opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, results = 'asis')
```

\vspace{-1cm}
\begin{center}
\href{mailto:john.broussard@rutgers.edu}{john.broussard@rutgers.edu} | 
\href{https://tinyurl.com/c3wdneyp}{Website} | 
\href{https://tinyurl.com/5bfex8hv}{LinkedIn} | 
ORCID: 0000-0002-5090-9947
\end{center}

\vspace{-0.3cm}
\noindent\rule{\textwidth}{0.5pt}

## Professional Summary

I am a Finance Professor with over 25 years of extensive domestic and international experience in online and traditional academic program management. I create academic programs and courses that monetize academic effort and yield institutional revenue enhancement and stakeholder success. I maintain real-world relevance through being a Financial Professional Designation Exam Trainer, Financial Risk Management Specialist, and Expert on AI/ML applications in Finance.

## Key Administrative Achievements

```{r admin-highlights}
if (exists("admin") && !is.null(admin)) {
  # Get top 3 admin roles
  admin_top <- admin %>%
    filter(highlight == TRUE) %>%
    arrange(display_order) %>%
    head(3)
  
  for (i in 1:nrow(admin_top)) {
    cat("\\textbf{", admin_top$title[i], "} -- ", admin_top$institution[i], "\n\n", sep = "")
    
    # Parse details if they're in a single field
    details <- strsplit(as.character(admin_top$detail[i]), ";")[[1]]
    cat("\\begin{itemize}[topsep=0pt, itemsep=0pt]\n")
    for (detail in details) {
      cat("\\item ", trimws(detail), "\n")
    }
    cat("\\end{itemize}\n\n")
  }
} else {
  cat("\\textbf{Director of Online MS Finance Program} -- University of Oklahoma\n\n")
  cat("\\begin{itemize}[topsep=0pt, itemsep=0pt]\n")
  cat("\\item Directed High Graduation Rate (>78\\%) Online Degree with approximately 150 students\n")
  cat("\\item Attained CFA Institute University Affiliation Program status\n")
  cat("\\item Created Streamlined Admissions Process for Automatic and Accelerated Admission Decisions\n")
  cat("\\end{itemize}\n\n")
}
```

## Education

**Ph.D., Finance** (1991-1995) -- Louisiana State University, Baton Rouge, LA  
**MBA, Finance** (1988-1991) -- Millsaps College, Jackson, MS  
**B.S., Biochemistry** (1981-1985) -- Louisiana State University, Baton Rouge, LA

## Professional Certifications

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item \textbf{Chartered Financial Analyst (CFA)} -- CFA Institute, 1997
\item \textbf{Financial Risk Manager (FRM)} -- Global Association of Risk Professionals, 1999  
\item \textbf{Professional Risk Manager (PRM)} -- PRMIA, 2003
\end{itemize}

## Current Academic Appointments

```{r current-positions}
cat("\\begin{itemize}[topsep=0pt, itemsep=0pt]\n")
cat("\\item \\textbf{Associate Professor of Finance} -- SUNY Empire State University (August 2025 - Present)\n")
cat("\\item \\textbf{Professor Emeritus} -- Rutgers University (2018 - Present)\n")
cat("\\item \\textbf{Visiting Professor} -- Estonian Business School (October 2024 - Present)\n")
cat("\\item \\textbf{International Lecturer} -- ZHAW School of Management and Law, Switzerland (July 2024 - Present)\n")
cat("\\end{itemize}\n\n")
```

## Selected Recent Publications

```{r publications}
if (exists("publications") && !is.null(publications)) {
  pubs_recent <- publications %>%
    filter(year >= 2018) %>%
    arrange(desc(year)) %>%
    head(5)
  
  cat("\\begin{itemize}[topsep=0pt, itemsep=2pt]\n")
  for (i in 1:nrow(pubs_recent)) {
    cat("\\item ", pubs_recent$authors[i], " (", pubs_recent$year[i], "). ",
        "\\textbf{", pubs_recent$title[i], "}. ",
        "\\textit{", pubs_recent$journal[i], "}.\n", sep="")
  }
  cat("\\end{itemize}\n\n")
} else {
  cat("\\begin{itemize}[topsep=0pt, itemsep=2pt]\n")
  cat("\\item Nikiforov, A., Osmekhin, S., \\& \\textbf{Broussard, J.P.} (2025). ")
  cat("\\textbf{The Market Ecosystem in the Age of Algorithms}. ")
  cat("\\textit{Journal of Economics and Finance}.\n")
  cat("\\item Vaihekoski, M. \\& \\textbf{Broussard, J.P.} (2022). ")
  cat("\\textbf{Time-variation of Dual-class Premia}. ")
  cat("\\textit{Nordic Journal of Business}, 71(1), 26-50.\n")
  cat("\\end{itemize}\n\n")
}
```

## Key Competencies

\begin{itemize}[topsep=0pt, itemsep=0pt]
\item \textbf{Administrative:} Program Development, Strategic Planning, Budget Management, Enrollment Strategy
\item \textbf{Teaching:} Online/Hybrid Course Design, Financial Modeling, Risk Management, FinTech/AI Applications  
\item \textbf{Research:} Market Microstructure, Algorithmic Trading, Machine Learning in Finance, Corporate Finance
\item \textbf{Professional:} CFA/FRM Exam Training, Industry Consulting, Financial Risk Management
\end{itemize}
