---
title: "John Paul Broussard"
subtitle: "Curriculum Vitae"
format:
  pdf:
    documentclass: article
    geometry:
      - margin=1in
    fontsize: 11pt
    include-in-header:
      text: |
        \usepackage{titlesec}
        \titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
        \titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}
execute:
  echo: false
  warning: false
  message: false
---

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(here)

# Load CV data
if (file.exists("jpbsCVdata/load_cv_data.r")) {
  source("jpbsCVdata/load_cv_data.r")
  cv_data <- load_cv_data()
  list2env(cv_data, envir = .GlobalEnv)
}
```

# John Paul Broussard

**Finance Professor with Decades of Superior Administrative, Research, and Teaching Experiences**

Willis, Texas, USA  
Email: john.broussard@rutgers.edu  
LinkedIn: tinyurl.com/5bfex8hv  
ORCID: 0000-0002-5090-9947  

---

## Professional Summary

I am a Finance Professor with over 25 years of extensive domestic and international experience in online and traditional academic program management. I create academic programs and courses that monetize academic effort and yield institutional revenue enhancement and stakeholder success.

## Administrative Experience

```{r admin, results='asis'}
if (exists("admin") && !is.null(admin)) {
  admin_highlight <- admin %>%
    filter(highlight == TRUE) %>%
    arrange(display_order)
  
  for (i in 1:nrow(admin_highlight)) {
    cat("### ", admin_highlight$title[i], "\n\n")
    cat("*", admin_highlight$institution[i], "*\n\n")
    cat("-", admin_highlight$detail[i], "\n\n")
  }
} else {
  cat("### Director of Online MS Finance Program\n\n")
  cat("*University of Oklahoma*\n\n")
  cat("- Directed High Graduation Rate (>78%) Online Degree with approximately 150 students\n")
  cat("- Attained CFA Institute University Affiliation Program status\n\n")
}
```

## Education

```{r education, results='asis'}
cat("### Ph.D., Finance (1991-1995)\n")
cat("*Louisiana State University, Baton Rouge, LA*\n\n")

cat("### MBA, Finance (1988-1991)\n")
cat("*Millsaps College, Jackson, MS*\n\n")

cat("### B.S., Biochemistry (1981-1985)\n")
cat("*Louisiana State University, Baton Rouge, LA*\n\n")
```

## Professional Certifications

- **Chartered Financial Analyst (CFA)** - CFA Institute, 1997
- **Financial Risk Manager (FRM)** - GARP, 1999
- **Professional Risk Manager (PRM)** - PRMIA, 2003

## Current Appointments

```{r employment, results='asis'}
cat("### Associate Professor of Finance\n")
cat("*SUNY - Empire State University* (August 2025 - Present)\n\n")

cat("### Professor Emeritus\n")
cat("*Rutgers University* (2018 - Present)\n\n")

cat("### Visiting Professor\n")
cat("*Estonian Business School* (October 2024 - Present)\n\n")
```

## Selected Publications

```{r publications, results='asis'}
if (exists("publications") && !is.null(publications)) {
  recent_pubs <- publications %>%
    filter(year >= 2020) %>%
    arrange(desc(year)) %>%
    head(5)
  
  for (i in 1:nrow(recent_pubs)) {
    cat("- ", recent_pubs$authors[i], " (", recent_pubs$year[i], "). ",
        "**", recent_pubs$title[i], "**. ",
        "*", recent_pubs$journal[i], "*.\n\n", sep="")
  }
} else {
  cat("- Publications list available upon request\n\n")
}
```
